---
title: "1.Master_Data"
output: html_notebook
---

#Script Description 

The purpose of this script is to consolidate data sourced from multiple published papers/data sets into a master file. 

# Packages Used

```{r, message=FALSE}

library(foreign)
library(tidyverse)
library(readxl)
library(haven)
library(curl)
library(dplyr)



```


# Data set 1 - Work Hour Elasticity 

This dataset is derived from the paper "How Hours Worked Vary with Income? Cross-Country Evidence and Implications" by Bick, Fuchs-Schündeln, and Lagakos (2017). It provides country-level estimates of labor supply elasticity, capturing how hours worked respond to changes in wages across different economies. 

```{r}


htw_elasticity <- read_dta("Data/Extracted_Data/elasticity_country_level.dta")

# Load master statistics data to obtain country names
bick_elasticity_master_stats <- read.dta("Data/Extracted_Data/elasticity_master_stats.dta") %>%
  select(country, countryname) #selecting relevant variables

# Merge elasticity data with master statistics to add country names
htw_elasticity <- htw_elasticity %>%
  left_join(bick_elasticity_master_stats, by = "country") %>% #joining datasets by country code
  rename(elasticity_male = beta_m, # Rename beta_m to elasticity_male for clarity
         elasticity_female = beta_f, # Rename beta_f to elasticity_female for clarity
         country_code = country) %>% # Rename country to country_code for better readability
  select(countryname, everything()) %>% # Ensure countryname is the first column
  filter(!country_code %in% c("USA-1895", "USA-1973", "USA-1991")) # exclude irrelevant rows

```


# Data Set 2 - Cultural Distance

This dataset is derived from "Beyond Western, Educated, Industrial, Rich, and Democratic (WEIRD) Psychology: Measuring and Mapping Scales of Cultural and Psychological Distance" by Muthukrishna et al. (2020). It provides country-level measures of cultural and psychological distance, quantifying differences between societies based on cognitive, social, and behavioral factors. The data includes cultural distance metrics relative to the U.S. and China. 


```{r}

# Load cultural distance data for the U.S. and China from an Excel file
cfst_data_us_china <- read_excel("Data/Extracted_Data/cultural_distance_US_America.xlsx")

# Rename the 'Country' column to 'countryname' for consistency across datasets
cfst_data_us_china_clean <- cfst_data_us_china %>% 
  rename(countryname = Country)

```


# Data Set 3 - World Management Survey 

This dataset is derived from the World Management Survey (WMS) and focuses on two key aspects of workplace management: performance culture (Section 15) and talent management (Section 14). Performance culture measures how firms implement goal-setting, accountability, and evaluation mechanisms, while talent management assesses hiring, training, and workforce development practices. The data is aggregated at the country level, providing mean scores for these dimensions.

```{r}

# Load Workplace Management Survey (WMS) data from a CSV file
wms_data <- read_csv("Data/Extracted_Data/wmsdata_2004_2015.csv")

# Clean and summarize WMS data
wms_data_clean <-
  wms_data %>% 
  select(country, talent2, talent3) %>%  # Select relevant columns
  group_by(country) %>% # Group data by country
  summarize("bonus_culture_prevalence" = mean(talent2, na.rm = TRUE), # Compute the mean of talent2 for performance culture
            "shirk_tolerance" = mean(talent3, na.rm = TRUE) # Compute the mean of talent3 for talent management
            ) %>%
  rename(countryname = country) # Rename country column for consistency


# --- Sample Size Calculations for Summary Table ---

# Calculate the total sample size by summing 'N' across all entries
summarize(wms_data, total_sample = sum(N))

# Count the number of unique countries in the dataset
length(unique(wms_data$country))

# Calculate the total sum of 'N' for each country
wms_data %>%
  group_by(country) %>%
  summarise(total_sum = sum(N, na.rm = TRUE))
```

#Data set 4 - Tightness-Looseness score for Non-industrial Countries 

This dataset is derived from "A Global Analysis of Cultural Tightness in Non-Industrial Societies" by Jackson, Gelfand, and Ember (2020). It provides measures of cultural tightness-looseness across non-industrial societies, capturing the extent to which social norms are strictly enforced and deviance is tolerated. 

```{r}

# Load non-industrial tightness-looseness data from a CSV file
nonindustrial_social_tightness <- read.csv("Data/Extracted_Data/non-industrial_tightness.csv")
  

```

#Data set 5 - GDP per Capita

This dataset is sourced from the World Bank and provides GDP per capita estimates for countries worldwide. 

```{r}

# Load GDP per capita data from the World Bank CSV file, skipping the first 4 rows (metadata)
gdp_wb <- read.csv("Data/Extracted_Data/gdp_per_capita_WB.csv", 
                   skip = 4)

# Clean and rename GDP dataset
gdp_wb_clean <-  
  gdp_wb %>%
  select(Country.Name, X2020, X2021) %>% # Select relevant columns for GDP per capita in 2020 and 2021
  rename( countryname = Country.Name, # Standardize country name column
          gdp_pc_2020 = X2020, # Rename GDP per capita for 2020
          gdp_pc_2021 = X2021) # Rename GDP per capita for 2021

# Load World Bank metadata containing country income classifications
country_income_class_wb <- read_csv("Data/Extracted_Data/incomeclass_WB.csv")%>%
  select(TableName, IncomeGroup) %>% # Select relevant columns
  rename(countryname = TableName) # Standardize country name column for merging

# Merge GDP data with income group classifications
gdp_wb_clean <- gdp_wb_clean %>%
  right_join(country_income_class_wb, by = "countryname") %>%
  filter(!is.na(IncomeGroup))  # Remove any rows where income classification is missing

```


#Data Set 6 - Tightness-Looseness score for Industrial Countries 


This dataset is derived from "Differences Between Tight and Loose Cultures: A 33-Nation Study" by Gelfand et al. (2011). It provides tightness-looseness scores for 33 countries, measuring the degree to which societies enforce social norms and tolerate deviation. Tighter cultures exhibit strong norms and lower tolerance for deviant behavior, while looser cultures allow for greater flexibility and individual expression.


```{r}

# Load industrial societal norm tightness data from an Excel file
industrial_social_tightness <- read_excel("Data/Extracted_Data/industrual_tightness.xlsx")

#cleaning the dataset 
industrial_tightness_clean <- industrial_social_tightness %>%
  select(Nation, `Tightness score`) %>% #selecting relevant columns 
  rename(countryname = Nation, # Standardize country name column
         tightness_score = `Tightness score`) # Rename tightness score column for clarity

# Remove the 33rd row from the dataset which is a total columns so its irrelevant
industrial_tightness_clean <- industrial_tightness_clean[-33, ]
  
```


#Data set 7 - Economic Preferences 

This dataset is derived from "Global Evidence on Economic Preferences" by Falk et al. (2018). It provides country-level measures of economic preferences, including patience, risk-taking, positive and negative reciprocity, altruism, and trust. 

```{r}

# Load economic preferences dataset from a .dta file
economic_preferences <-
  read_dta("Data/Extracted_Data/economicpreferences_country.dta")

# Clean and rename columns for consistency
economic_preferences_clean <- economic_preferences %>%
  rename(countryname = country,
         preferences_patience = patience,
         preferences_risktaking = risktaking,
         preferences_posrecip = posrecip,
         preferences_negrecip = negrecip,
         preferences_altruism = altruism,
         preferences_trust = trust,
         countrycode = isocode
         ) %>%
  select(-countrycode) # Removing repetitive column

```


# Data Set 8 - Responsibilism 

```{r}

responsibilism <- read_excel("Data/Extracted_Data/Responsibilism Country Scores.xlsx")  %>%
  rename(countryname = Culture)

```

# Data Set 9 - Universalism 

This data set is extracted from Universalism: Global Evidence by Cappelen, Enke and Tungodden (2025). It provided country level estimate of universalism. 

```{r}

universalism <- read_excel("Data/Extracted_Data/Universalism.xlsx")

```

# Data Set 10 - Total Factor Productivty 

```{r}

tfp <- read_excel("Data/Extracted_Data/penn_world_tables.xlsx", sheet = "Data") 

tfp_clean <- tfp %>%
  select(country, year, ctfp) %>%
  filter(year == 2019) %>%
  rename(countryname = country, 
         total_factor_productivity = ctfp) %>%
  select(countryname, total_factor_productivity) %>%
  drop_na()



```

# Data Set 11 - Individualism

```{r}

individualism <- read_csv("Data/Extracted_Data/individualism_culturaldistance.csv")

```

# Data Set 12 - Tightness_Looseness 

```{r}

tight_loose_cd <- read_excel("Data/Extracted_Data/tightness_looseness_culturaldistance.xlsx") %>%
  rename(tight_loose_cd = tight_loose)

```

# Translation Table 

The Translation Table file serves as a standardized mapping of country names across multiple datasets to ensure consistency in data consolidation. By aligning country names across datasets, it facilitates accurate merging and cross-country comparisons, ensuring that data from different sources can be integrated seamlessly.

```{r}

# Load the country translation table from an Excel file
country_translation_table <- read_excel("Data/Extracted_Data/Translation_Table_Countries.xlsx")

```


# Consolidated Dataset 


This chunk of code matches each dataset to the translation table, standardizing country names where discrepancies exist. The cleaned datasets are then merged into a consolidated dataset containing all extracted variables. Finally, the script removes redundant country code columns, organizes the data for clarity, and ensures that only countries with valid data are retained.


```{r}

# Standardizing country names in the htw_elasticity dataset
htw_elasticity <- htw_elasticity %>%
  left_join(country_translation_table %>% 
              select("elasticity", "universal_name", "ISO_code"), by = c("countryname" = "elasticity")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the cultural distance dataset
cfst_data_us_china_clean <- cfst_data_us_china_clean %>%
  left_join(country_translation_table %>% 
              select("cultural_distance", "universal_name", "ISO_code"), by = c("countryname" = "cultural_distance")) %>% 
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the workplace management survey (WMS) dataset
wms_data_clean <- wms_data_clean %>%
  left_join(country_translation_table %>% 
              select("wms", "universal_name", "ISO_code"), by = c("countryname" = "wms")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the industrial tightness dataset
industrial_tightness_clean <- industrial_tightness_clean %>%
  left_join(country_translation_table %>% 
              select("industrial_tightness", "universal_name", "ISO_code"), by = c("countryname" = "industrial_tightness")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the GDP dataset
gdp_wb_clean <- gdp_wb_clean %>%
  left_join(country_translation_table %>% 
              select("gdp", "universal_name", "ISO_code"), by = c("countryname" = "gdp")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the economic preferences dataset
economic_preferences_clean <- economic_preferences_clean %>%
  left_join(country_translation_table %>% 
              select("economic_preferences", "universal_name", "ISO_code"), by = c("countryname" = "economic_preferences")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the responsibilism dataset
responsibilism_clean <- responsibilism %>%
  left_join(country_translation_table %>% 
              select("responsibilism", "universal_name", "ISO_code"), by = c("countryname" = "responsibilism")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the universalism dataset
universalism_clean <- universalism %>%
  left_join(country_translation_table %>% 
              select("universalism", "universal_name", "ISO_code"), by = c("countryname" = "universalism")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the TFP dataset
tfp_clean <- tfp_clean %>%
  left_join(country_translation_table %>% 
              select("tfp_names", "universal_name", "ISO_code"), by = c("countryname" = "tfp_names")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the Individualism dataset
individualism <- individualism %>%
  left_join(country_translation_table %>% 
              select("Individualism", "universal_name", "ISO_code"), by = c("countryname" = "Individualism")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column

# Standardizing country names in the Tight-Loose Distance dataset
tight_loose_cd <- tight_loose_cd %>%
  left_join(country_translation_table %>% 
              select("Individualism", "universal_name", "ISO_code"), by = c("countryname" = "Individualism")) %>%
  mutate(countryname = if_else(!is.na(universal_name), universal_name, countryname)) %>% #replace countryname with universal name
  select(-universal_name) # Remove the temporary universal name column


# --- Consolidating all datasets into one master dataset ---
combined_data <- 
  full_join(htw_elasticity, cfst_data_us_china_clean, by = c("countryname", "ISO_code")) %>%
  full_join(wms_data_clean, by = c("countryname", "ISO_code")) %>%
  full_join(industrial_tightness_clean, by = c("countryname", "ISO_code")) %>%
  full_join(economic_preferences_clean, by = c("countryname", "ISO_code")) %>%
  full_join(responsibilism_clean, by = c("countryname", "ISO_code")) %>%
  full_join(universalism_clean, by = c("countryname", "ISO_code")) %>%
  full_join(tfp_clean, by = c("countryname", "ISO_code")) %>%
  full_join(individualism, by = c("countryname", "ISO_code")) %>%
  full_join(tight_loose_cd, by = c("countryname", "ISO_code")) %>%
  left_join(gdp_wb_clean, by = c("countryname", "ISO_code")) %>% # Left join to keep all previously matched data
  filter(!if_all(everything(), is.na)) # Remove rows where all values are missing


# --- Final Cleaning and Organization ---
combined_data <- combined_data %>% 
  select(-country_code) %>% # Remove redundant country_code column
  arrange(countryname, ISO_code) %>% # Sort by country name and ISO code
  select(countryname, ISO_code, everything()) # Ensure countryname and ISO_code appear first
 

```


# Calculating Pairwise overlap of Countries between datasets

This code identifies the number of overlapping countries across selected variables, ensuring that data availability is assessed for cross-country comparisons. It generates tables that count the number of shared observations for variable pairs, both overall and within different income groups. Additionally, it creates a detailed list of countries with available data for each variable pair, facilitating a structured analysis of data completeness.

```{r}

# Function to count overlapping countries for each pair of selected variables
count_overlapping_countries <- function(data, columns) {
  columns <- columns[columns %in% colnames(data)] # Ensure selected columns exist in the dataset
    results <- data.frame(Variable1 = character(), Variable2 = character(), Overlapping_Countries = integer())

  # Iterate over each pair of columns
  for (i in 1:(length(columns) - 1)) {
    for (j in (i + 1):length(columns)) {
      var1 <- columns[i]
      var2 <- columns[j]

      # Count the number of countries that have non-missing values for both variables
      count_overlap <- data %>%
        filter(!is.na(.data[[var1]]) & !is.na(.data[[var2]])) %>%
        nrow()
      results <- rbind(results, data.frame(Variable1 = var1, Variable2 = var2, Overlapping_Countries = count_overlap))
    }
  }
        # Store results in a dataframe

  return(results)
}

# Define the selected variables for overlap analysis
selected_columns <- c("elasticity_male", "america_cfst", "bonus_culture_prevalence", "tightness_score", "preferences_patience", "gdp_pc_2021", "Responsibilism", "total_factor_productivity", "composite_universalism", "Individualism", "tight_loose")

# Compute the overlap table
overlap_table <- count_overlapping_countries(combined_data, selected_columns)


# Function to count overlapping countries grouped by income classification
count_overlapping_countries_by_income <- function(data, columns, income_column) {
  columns <- columns[columns %in% colnames(data)]
  results <- data.frame(Variable1 = character(), Variable2 = character(), IncomeGroup = character(), Overlapping_Countries = integer())

  for (i in 1:(length(columns) - 1)) {
    for (j in (i + 1):length(columns)) {
      var1 <- columns[i]
      var2 <- columns[j]
      
      # Count the number of overlapping countries within each income group
      income_overlap <- data %>%
        filter(!is.na(.data[[var1]]) & !is.na(.data[[var2]])) %>%
        group_by(.data[[income_column]]) %>%
        summarise(Overlapping_Countries = n(), .groups = "drop") %>%
        mutate(Variable1 = var1, Variable2 = var2)

      results <- bind_rows(results, income_overlap)
    }
  }
  
  return(results)
}

# Define selected columns for income-based overlap analysis
selected_columns <- c("elasticity_male", "america_cfst", "bonus_culture_prevalence", "tightness_score", "preferences_patience", "Responsibilism", "total_factor_productivity", "composite_universalism", "Individualism", "tight_loose")
income_column <- "IncomeGroup"  

# Compute the overlap table by income classification
overlap_income_table <- count_overlapping_countries_by_income(combined_data, selected_columns, income_column)

# Rename variables for better readability in the final overlap table
overlap_table <- overlap_table %>%
  mutate(Variable1 = case_when(
    Variable1 == "elasticity_male" ~ "Elasticity", 
    Variable1 == "america_cfst" ~ "Cultural Distance", 
    Variable1 == "bonus_culture_prevalence" ~ "WMS", 
    Variable1 == "tightness_score" ~ "Industrial Tightness", 
    Variable1 == "preferences_patience" ~ "Economic Preferences",
    Variable1 == "gdp_pc_2021" ~ "GDP per Capita",
    TRUE ~ Variable1
  )) %>%
   mutate(Variable2 = case_when(
    Variable2 == "elasticity_male" ~ "Elasticity", 
    Variable2 == "america_cfst" ~ "Cultural Distance", 
    Variable2 == "bonus_culture_prevalence" ~ "WMS", 
    Variable2 == "tightness_score" ~ "Industrial Tightness", 
    Variable2 == "preferences_patience" ~ "Economic Preferences",
    Variable2 == "gdp_pc_2021" ~ "GDP per Capita",
    TRUE ~ Variable2
  ))


# Rename variables for better readability in the income-based overlap table
overlap_income_table <- overlap_income_table %>%
  mutate(Variable1 = case_when(
    Variable1 == "elasticity_male" ~ "Elasticity", 
    Variable1 == "america_cfst" ~ "Cultural Distance", 
    Variable1 == "bonus_culture_prevalence" ~ "WMS", 
    Variable1 == "tightness_score" ~ "Industrial Tightness", 
    Variable1 == "preferences_patience" ~ "Economic Preferences",
    TRUE ~ Variable1
  )) %>%
   mutate(Variable2 = case_when(
    Variable2 == "elasticity_male" ~ "Elasticity", 
    Variable2 == "america_cfst" ~ "Cultural Distance", 
    Variable2 == "bonus_culture_prevalence" ~ "WMS", 
    Variable2 == "tightness_score" ~ "Industrial Tightness", 
    Variable2 == "preferences_patience" ~ "Economic Preferences",
    TRUE ~ Variable2
  ))

# Function to create a table listing countries overlapping for each variable pair
find_overlapping_countries_table <- function(data, columns, country_column) {
  columns <- columns[columns %in% colnames(data)]
  

    results_list <- list()


      for (i in 1:(length(columns) - 1)) {
    for (j in (i + 1):length(columns)) {
      var1 <- columns[i]
      var2 <- columns[j]
      

          pair_name <- paste(var1, "vs", var2, sep = " ")
    
      # Identify countries with non-missing values for both variables
      overlapping_countries <- data %>%
        filter(!is.na(.data[[var1]]) & !is.na(.data[[var2]])) %>%
        select(all_of(country_column)) %>%
        distinct() %>%
        arrange(.data[[country_column]])  

      results_list[[pair_name]] <- overlapping_countries[[country_column]]
    }
  }
  
  # Convert results into a dataframe
  results_df <- as.data.frame(do.call(cbind, results_list))
  
  return(results_df)
}

# Define selected columns and country column for overlap analysis
selected_columns <- c("elasticity_male", "america_cfst", "bonus_culture_prevalence", "tightness_score", "preferences_patience", "Responsibilism", "total_factor_productivity", "composite_universalism", "Individualism", "tight_loose")
country_column <- "countryname"  


# Generate a table listing overlapping countries for each variable pair and rename for readability
overlap_countries_table <- find_overlapping_countries_table(combined_data, selected_columns, country_column) %>%
  rename( "Elasticity vs Cultural Distance" = "elasticity_male vs america_cfst",             
          "Elasticity vs WMS" = "elasticity_male vs bonus_culture_prevalence",
          "Elasticity vs Industrial Tightness" = "elasticity_male vs tightness_score",           
          "Elasticity vs Economic Preferences" = "elasticity_male vs preferences_patience",     
          "Cultural Distance vs WMS" = "america_cfst vs bonus_culture_prevalence",         
          "Cultural Distance vs Industrial Tightness" = "america_cfst vs tightness_score",            
          "Cultural Distance vs Economic Preferences" = "america_cfst vs preferences_patience",       
          "WMS vs Industrial Tightness" = "bonus_culture_prevalence vs tightness_score",     
          "WMS vs Economic Preferences" = "bonus_culture_prevalence vs preferences_patience", 
          "Elasticity vs Responsibilism" = "elasticity_male vs Responsibilism",
          "Cultural Distance vs Responsibilism" = "america_cfst vs Responsibilism",
          "WMS vs Responsibilism" = "bonus_culture_prevalence vs Responsibilism",
          "Industrual Tightness vs Responsibilism" = "tightness_score vs Responsibilism",
          "Economic Preferences vs Responsibilism" = "preferences_patience vs Responsibilism")



```

# Exporting outputs

This code exports the consolidated dataset and overlap analysis tables to separate Excel files for further analysis and documentation.

```{r}

# Save the consolidated dataset and overlap tables to Excel
library(writexl)
write_xlsx(combined_data, path = "Data/Generated_Data/Master_Data.xlsx")

# Create a list of data frames to store as separate sheets in an Excel file
sheets_list <- list(
  "Overlap Table" = overlap_table,
  "Overlap Income Table" = overlap_income_table,
  "Overlap Countries Table" = overlap_countries_table
)

# Write all overlap tables into an Excel file
write_xlsx(sheets_list, path = "Tables/Pairwise_Tables.xlsx")
```
