---
title: "Regression Tables"
output: html_notebook
Author: "Ayesha Zafar" 
---


#Script Description 

The purpose of this script is to create a regression table 


# Packages Used

```{r, message=FALSE}

library(tidyverse)
library(stargazer)
library(ggpubr)
library(readxl)
library(tinytex)
library(texreg)
library(lmtest)
library(sandwich)

```

# Load Dataset 

The master data is consolidated using the 1.Master_Data.RMD script. Wms data is extracted from the World Management Survey public data. 

```{r, message=FALSE}

master_data <- read_excel("Data/Generated_Data/Master_Data.xlsx") %>%
  mutate(LogGDP = log(gdp_pc_2021))

#Loading Firm Level Data 

wms_data <- read_csv("Data/Extracted_Data/wmsdata_2004_2015.csv") %>%
  select(country, talent2, talent3, sic2, employment) %>%  # Select relevant columns %>%
  rename("bonus_firm" = "talent2", 
         "shirk_firm" = "talent3", 
         "countryname" = "country") %>%
  mutate(bonus_culture_prevalence_firm = ifelse(bonus_firm >= 4, 1,0),
         shirk_tolerance_firm = ifelse(shirk_firm >= 4, 1,0))

wms_data$employment <- factor(wms_data$employment,
                                 levels = c("A) 50 to 100",
                                            "B) 101 to 250",
                                            "C) 251 to 500",
                                            "D) 501 to 1000",
                                            "E) 1000+"))

wms_combined <- merge(wms_data, master_data, by = "countryname", all.x = TRUE) %>%
  mutate(countryname = as.character(countryname))


```


# Calculating Medians & Mean

This chunk of code is calculating Medians of all cultural variables, and then recoding the variables as Dummys, with 1 above median. This is to ensure consistency of interpretation. 

Means are calculated to add in the final regression tables
```{r}

responsibilism_median <- master_data %>% 
  filter(!is.na(Responsibilism)) %>%
  pull(Responsibilism) %>%
  median()
  
universalism_median <- master_data %>% 
  filter(!is.na(domestic_universalism)) %>%
  pull(domestic_universalism) %>%
  median()
  
  
individualism_median <- master_data %>% 
  filter(!is.na(Individualism)) %>%
  pull(Individualism) %>%
  median()
  
tightloose_median <-master_data %>% 
  filter(!is.na(tight_loose_cd)) %>%
  pull(tight_loose_cd) %>%
  median()

master_data <- master_data %>%
  mutate(dummy_responsibilism = ifelse(Responsibilism <= responsibilism_median, 1, 0), #coded below median to be closer to weird cultures for consistency 
         dummy_universalism = ifelse(domestic_universalism >= universalism_median, 1, 0), 
         dummy_individualism = ifelse(Individualism >= individualism_median, 1, 0), 
         dummy_tightloose = ifelse(tight_loose_cd >= tightloose_median, 1, 0))

wms_combined <- wms_combined %>%
  mutate(dummy_responsibilism = ifelse(Responsibilism <= responsibilism_median, 1, 0), #coded below median to be closer to weird cultures for consistency 
         dummy_universalism = ifelse(domestic_universalism >= universalism_median, 1, 0), 
         dummy_individualism = ifelse(Individualism >= individualism_median, 1, 0), 
         dummy_tightloose = ifelse(tight_loose_cd >= tightloose_median, 1, 0))

mean_wms <- 
  summarise(wms_combined, bonusmean = mean(bonus_culture_prevalence_firm, na.rm=TRUE),
            shirkmean = mean(shirk_tolerance_firm, na.rm = TRUE))
  
means <- summarise(master_data, tfpmean = mean(total_factor_productivity, na.rm=TRUE), elasticitymean = mean(elasticity_male, na.rm=TRUE))



```



# Running the Single Variate Models

This chunk is creating single variate models for 4 dependent variables, TFP, Bonus Culture, Shirk Tolerance and Wage Elasticity

```{r}

 models_TFP <- list(
  lm(total_factor_productivity ~ dummy_responsibilism, 
     data=master_data),
  lm(total_factor_productivity ~ dummy_universalism, 
     data=master_data),
  lm(total_factor_productivity ~ dummy_individualism, 
     data=master_data), 
  lm(total_factor_productivity ~ dummy_tightloose, 
     data=master_data))

# LM with Fixed effects for employment and industry, with SE clustered at country level

models_bonus_wms <- list(
  lm(bonus_culture_prevalence_firm ~ dummy_responsibilism + LogGDP + employment + factor(sic2), 
     data = wms_combined),
  
  lm(bonus_culture_prevalence_firm ~ dummy_universalism +  LogGDP + employment + factor(sic2), 
     data = wms_combined),
  
  lm(bonus_culture_prevalence_firm ~ dummy_individualism +  LogGDP + employment + factor(sic2), 
     data = wms_combined),
  
  lm(bonus_culture_prevalence_firm ~ dummy_tightloose +  LogGDP + employment + factor(sic2), 
     data = wms_combined))


# LM with Fixed effects for employment and industry, LogGDP as control with SE clustered at country level

models_shirk_wms <- list(
  lm(shirk_tolerance_firm ~ dummy_responsibilism +  LogGDP + employment + factor(sic2), 
       data = wms_combined),
  
  lm(shirk_tolerance_firm ~ dummy_universalism + LogGDP +  employment + factor(sic2), 
       data = wms_combined),
  
  lm(shirk_tolerance_firm ~ dummy_individualism +  LogGDP + employment + factor(sic2), 
       data = wms_combined),
  
  lm(shirk_tolerance_firm ~ dummy_tightloose + LogGDP + employment + factor(sic2), 
       data = wms_combined))


models_Elasticity <- list(
  lm(elasticity_male ~ dummy_responsibilism + LogGDP, 
     data=master_data),
  lm(elasticity_male ~ dummy_universalism + LogGDP, 
     data=master_data),
  lm(elasticity_male ~ dummy_individualism + LogGDP, 
     data=master_data),
  lm(elasticity_male ~ dummy_tightloose + LogGDP, 
     data=master_data))

```


# Running the Multi-Variate Models 

This chunk is running 4 multivariate models. 

```{r}

# Run a Multivariate Model for each outcome

multi_TFP <- lm(total_factor_productivity ~ dummy_responsibilism + dummy_universalism + dummy_individualism + dummy_tightloose, 
                data= master_data)

models_TFP <- c(models_TFP, list(multi_TFP))


multi_WMS_bonus <- lm(bonus_culture_prevalence_firm ~ dummy_responsibilism + dummy_universalism + dummy_individualism + dummy_tightloose + LogGDP + employment + factor(sic2)
                      , data = wms_combined)
 
multi_WMS_shirk <- lm(shirk_tolerance_firm ~ dummy_responsibilism + dummy_universalism + dummy_individualism + dummy_tightloose + LogGDP + employment + factor(sic2)
                      , data = wms_combined)


models_bonus_wms <- c(models_bonus_wms, list(multi_WMS_bonus))

models_shirk_wms <- c(models_shirk_wms, list(multi_WMS_shirk))

multi_Elasticity <- lm(elasticity_male ~ dummy_responsibilism + dummy_universalism + dummy_individualism + dummy_tightloose, 
                       data=master_data)

models_Elasticity <- c(models_Elasticity, list(multi_Elasticity))


```


# Spearman Test 

This chunk is computing spearman correlations for all of the single variate models and saving them to include in the final regression table. 

```{r}


# Compute Spearman correlations for each model

TFP_Resp = cor.test( y = master_data$total_factor_productivity, 
                     x = master_data$dummy_responsibilism, 
                     method = "spearman")

TFP_Uni = cor.test( y = master_data$total_factor_productivity, 
                    x = master_data$dummy_universalism, 
                    method = "spearman")

TFP_Ind = cor.test( y = master_data$total_factor_productivity, 
                    x = master_data$dummy_individualism, 
                    method = "spearman")

TFP_TL = cor.test( y = master_data$total_factor_productivity, 
                    x = master_data$dummy_tightloose, 
                    method = "spearman")

# Saving the Values to add to final regression table

TFP_spearman_values <- list(
  "Spearman Correlation (Responsibilism)" = round(TFP_Resp$estimate, 3),
  "P-Value (Responsibilism)" = round(TFP_Resp$p.value, 3),
  
  "Spearman Correlation (Universalism)" = round(TFP_Uni$estimate, 3),
  "P-Value (Universalism)" = round(TFP_Uni$p.value, 3), 
  
  "Spearman Correlation (Individualism)" = round(TFP_Ind$estimate, 3),
  "P-Value (Individualism)" = round(TFP_Ind$p.value, 3),
  
  "Spearman Correlation (Tightness-Looseness)" = round(TFP_TL$estimate, 3),
  "P-Value (Tightness-Looseness)" = round(TFP_TL$p.value, 3)
)

bonus_Resp = cor.test( y = master_data$bonus_culture_prevalence, 
                     x = master_data$dummy_responsibilism, 
                     method = "spearman")

bonus_Uni = cor.test( y = master_data$bonus_culture_prevalence, 
                    x = master_data$dummy_universalism, 
                    method = "spearman")

bonus_Ind = cor.test( y = master_data$bonus_culture_prevalence, 
                    x = master_data$dummy_individualism, 
                    method = "spearman")

bonus_TL = cor.test( y = master_data$bonus_culture_prevalence, 
                    x = master_data$dummy_tightloose, 
                    method = "spearman")

Bonus_spearman_values <- list(
  "Spearman Correlation (Responsibilism)" = round(bonus_Resp$estimate, 3),
  "P-Value (Responsibilism)" = round(bonus_Resp$p.value, 3),
  
  "Spearman Correlation (Universalism)" = round(bonus_Uni$estimate, 3),
  "P-Value (Universalism)" = round(bonus_Uni$p.value, 3),
  
  "Spearman Correlation (Individualism)" = round(bonus_Ind$estimate, 3),
  "P-Value (Individualism)" = round(bonus_Ind$p.value, 3),
  
  "Spearman Correlation (Tightness-Looseness)" = round(bonus_TL$estimate, 3),
  "P-Value (Tightness-Looseness)" = round(bonus_TL$p.value, 3)
)

shirk_Resp = cor.test( y = master_data$shirk_tolerance, 
                     x = master_data$dummy_responsibilism, 
                     method = "spearman")

shirk_Uni = cor.test( y = master_data$shirk_tolerance, 
                    x = master_data$dummy_universalism, 
                    method = "spearman")

shirk_Ind = cor.test( y = master_data$shirk_tolerance, 
                    x = master_data$dummy_individualism, 
                    method = "spearman")

shirk_TL = cor.test( y = master_data$shirk_tolerance, 
                    x = master_data$dummy_tightloose, 
                    method = "spearman")

Shirk_spearman_values <- list(
  "Spearman Correlation (Responsibilism)" = round(shirk_Resp$estimate, 3),
  "P-Value (Responsibilism)" = round(shirk_Resp$p.value, 3),
  
  "Spearman Correlation (Universalism)" = round(shirk_Uni$estimate, 3),
  "P-Value (Universalism)" = round(shirk_Uni$p.value, 3),
  
  "Spearman Correlation (Individualism)" = round(shirk_Ind$estimate, 3),
  "P-Value (Individualism)" = round(shirk_Ind$p.value, 3),
  
  "Spearman Correlation (Tightness-Looseness)" = round(shirk_TL$estimate, 3),
  "P-Value (Tightness-Looseness)" = round(shirk_TL$p.value, 3)
)


Elasticity_Resp = cor.test( y = master_data$elasticity_male, 
                            x = master_data$dummy_responsibilism,
                            method = "spearman")

Elasticity_Uni = cor.test( y = master_data$elasticity_male, 
                       x = master_data$dummy_universalism, 
                       method = "spearman")

Elasticity_Ind = cor.test( y = master_data$elasticity_male, 
                    x = master_data$dummy_individualism, 
                    method = "spearman")

Elasticity_TL = cor.test( y = master_data$elasticity_male, 
                    x = master_data$dummy_tightloose, 
                    method = "spearman")

Elasticity_spearman_values <- list(
  "Spearman Correlation (Responsibilism)" = round(Elasticity_Resp$estimate, 3),
  "P-Value (Responsibilism)" = round(Elasticity_Resp$p.value, 3),
  
  "Spearman Correlation (Universalism)" = round(Elasticity_Uni$estimate, 3),
  "P-Value (Universalism)" = round(Elasticity_Uni$p.value, 3), 
  
  "Spearman Correlation (Individualism)" = round(Elasticity_Ind$estimate, 3),
  "P-Value (Individualism)" = round(Elasticity_Ind$p.value, 3), 
  
  "Spearman Correlation (Tightness-Looseness)" = round(Elasticity_TL$estimate, 3),
  "P-Value (Tightness-Looseness)" = round(Elasticity_TL$p.value, 3)
)

```

# Calculating Base Rate

```{r}

get_base_rate <- function(df, dep_var, dummy_var) {
  df %>%
    filter(!is.na(.data[[dep_var]]), !is.na(.data[[dummy_var]])) %>%
    summarise(mean_value = mean(.data[[dep_var]], na.rm = TRUE)) %>%
    pull(mean_value)
}

get_base_rate_combined <- function(df, dep_var, dummy_vars) {
  df %>%
    filter(
      !is.na(.data[[dep_var]]),
      across(all_of(dummy_vars), ~ !is.na(.x)) %>% rowSums() == length(dummy_vars)
    ) %>%
    summarise(mean_value = mean(.data[[dep_var]], na.rm = TRUE)) %>%
    pull(mean_value)
}


base_rates_bonus <- list(
base_rate_bonus_responsibilism = get_base_rate(wms_combined, "bonus_culture_prevalence_firm", "dummy_responsibilism"),
base_rate_bonus_universalism   = get_base_rate(wms_combined, "bonus_culture_prevalence_firm", "dummy_universalism"),
base_rate_bonus_individualism  = get_base_rate(wms_combined, "bonus_culture_prevalence_firm", "dummy_individualism"),
base_rate_bonus_tightloose     = get_base_rate(wms_combined, "bonus_culture_prevalence_firm", "dummy_tightloose"),
base_rate_bonus_combined = get_base_rate_combined(
  df = wms_combined,
  dep_var = "bonus_culture_prevalence_firm",
  dummy_vars = c("dummy_responsibilism", "dummy_universalism", "dummy_individualism", "dummy_tightloose")
))


base_rates_shirk <- list(
  base_rate_shirk_responsibilism = get_base_rate(wms_combined, "shirk_tolerance_firm", "dummy_responsibilism"),
  base_rate_shirk_universalism   = get_base_rate(wms_combined, "shirk_tolerance_firm", "dummy_universalism"),
  base_rate_shirk_individualism  = get_base_rate(wms_combined, "shirk_tolerance_firm", "dummy_individualism"),
  base_rate_shirk_tightloose     = get_base_rate(wms_combined, "shirk_tolerance_firm", "dummy_tightloose"),
  base_rate_shirk_combined = get_base_rate_combined(
  df = wms_combined,
  dep_var = "shirk_tolerance_firm",
  dummy_vars = c("dummy_responsibilism", "dummy_universalism", "dummy_individualism", "dummy_tightloose")
))


base_rates_tfp <- list(
  base_rate_tfp_responsibilism = get_base_rate(master_data, "total_factor_productivity", "dummy_responsibilism"),
  base_rate_tfp_universalism   = get_base_rate(master_data, "total_factor_productivity", "dummy_universalism"),
  base_rate_tfp_individualism  = get_base_rate(master_data, "total_factor_productivity", "dummy_individualism"),
  base_rate_tfp_tightloose     = get_base_rate(master_data, "total_factor_productivity", "dummy_tightloose"),
  base_rate_tfp_combined = get_base_rate_combined(
  df = wms_combined,
  dep_var = "total_factor_productivity",
  dummy_vars = c("dummy_responsibilism", "dummy_universalism", "dummy_individualism", "dummy_tightloose")
))

base_rates_elasticity <- list(
  base_rate_elasticity_responsibilism = get_base_rate(master_data, "elasticity_male", "dummy_responsibilism"),
  base_rate_elasticity_universalism   = get_base_rate(master_data, "elasticity_male", "dummy_universalism"),
  base_rate_elasticity_individualism  = get_base_rate(master_data, "elasticity_male", "dummy_individualism"),
  base_rate_elasticity_tightloose     = get_base_rate(master_data, "elasticity_male", "dummy_tightloose"),
  base_rate_elasticity_combined = get_base_rate_combined(
  df = wms_combined,
  dep_var = "elasticity_male",
  dummy_vars = c("dummy_responsibilism", "dummy_universalism", "dummy_individualism", "dummy_tightloose")
))

```


# Creating the Regression Table

This chunk is creating the regression table and saving each table to a tex file. 

```{r, warning=FALSE}

# TFP Models Summary

stargazer(models_TFP, 
          type = "latex",
          title = "TFP Regression Results",
          float = FALSE,
          dep.var.labels = "TFP",
          covariate.labels = c("Relatively Low Responsibilism", 
                               "Relatively High Universalism ", 
                               "Relatively Individualistic", 
                               "Relatively Loose"),
          omit = c("Constant"),
          add.lines = list(
            c("Base Rate (TFP)", 
              round(base_rates_tfp$base_rate_tfp_responsibilism, 3),
              round(base_rates_tfp$base_rate_tfp_universalism, 3),
              round(base_rates_tfp$base_rate_tfp_individualism, 3),
              round(base_rates_tfp$base_rate_tfp_tightloose, 3),
              round(base_rates_tfp$base_rate_tfp_combined, 3)),
            c("Spearman Correlation", 
              TFP_spearman_values[["Spearman Correlation (Responsibilism)"]],
              TFP_spearman_values[["Spearman Correlation (Universalism)"]],
              TFP_spearman_values[["Spearman Correlation (Individualism)"]],
              TFP_spearman_values[["Spearman Correlation (Tightness-Looseness)"]],
              "NA"),
            c("P-Value", 
              TFP_spearman_values[["P-Value (Responsibilism)"]],
              TFP_spearman_values[["P-Value (Universalism)"]],
              TFP_spearman_values[["P-Value (Individualism)"]],
              TFP_spearman_values[["P-Value (Tightness-Looseness)"]],
              "N/A")
          ),
          out = "Tables/Regressions/tfp_models_combined.tex")


# Elasticity Models Summary

stargazer(models_Elasticity, 
          type = "latex",
          title = "Elasticity Regression Results",
          float = FALSE,
          dep.var.labels = "Male Hour-Wage Elasticty",
          covariate.labels = c("Relatively Low Responsibilism", 
                               "Relatively High Universalism ", 
                               "Relatively Individualistic", 
                               "Relatively Loose"),
          omit = c("Constant"),
          add.lines = list(
            c("Base Rate (Male Wage Elasticity)", 
              round(base_rates_elasticity$base_rate_elasticity_responsibilism, 3),
              round(base_rates_elasticity$base_rate_elasticity_universalism, 3),
              round(base_rates_elasticity$base_rate_elasticity_individualism, 3),
              round(base_rates_elasticity$base_rate_elasticity_tightloose, 3),
              round(base_rates_elasticity$base_rate_elasticity_combined, 3)),
            c("Spearman Correlation", 
              Elasticity_spearman_values[["Spearman Correlation (Responsibilism)"]],
              Elasticity_spearman_values[["Spearman Correlation (Universalism)"]],
              Elasticity_spearman_values[["Spearman Correlation (Individualism)"]],
              Elasticity_spearman_values[["Spearman Correlation (Tightness-Looseness)"]],
              "N/A"),
            c("P-Value", 
              Elasticity_spearman_values[["P-Value (Responsibilism)"]],
              Elasticity_spearman_values[["P-Value (Universalism)"]],
              Elasticity_spearman_values[["P-Value (Individualism)"]],
              Elasticity_spearman_values[["P-Value (Tightness-Looseness)"]])
          ),
          out = "Tables/Regressions/elasticity_models_combined.tex")

```



```{r, warning=FALSE}

# Saving Country Observations

wms_country_observations <- list(
  Responsibilism = wms_combined %>%
    filter(!is.na(bonus_culture_prevalence_firm) & !is.na(dummy_responsibilism)) %>%
    distinct(countryname) %>%
    nrow(),
  
  Universalism = wms_combined %>%
    filter(!is.na(bonus_culture_prevalence_firm) & !is.na(dummy_universalism)) %>%
    distinct(countryname) %>%
    nrow(),
  
  Individualism = wms_combined %>%
    filter(!is.na(bonus_culture_prevalence_firm) & !is.na(dummy_individualism)) %>%
    distinct(countryname) %>%
    nrow(),
  
  Tightness = wms_combined %>%
    filter(!is.na(bonus_culture_prevalence_firm) & !is.na(dummy_tightloose)) %>%
    distinct(countryname) %>%
    nrow(),
  
  Combined = wms_combined %>%
    filter(!is.na(bonus_culture_prevalence_firm),
           !is.na(dummy_responsibilism),
           !is.na(dummy_universalism),
           !is.na(dummy_individualism),
           !is.na(dummy_tightloose)) %>%
    distinct(countryname) %>%
    nrow()
)

wms_firm_obs <- sapply(models_bonus_wms, nobs)

# Clustered SE at country level For bonus prevalence models
clustered_se_bonus <- lapply(c(models_bonus_wms, list(multi_WMS_bonus)), function(model) {
  coeftest(model, vcov = vcovCL(model, cluster = ~countryname, data = wms_combined))
})

coef_list_bonus <- lapply(clustered_se_bonus, function(x) x[, "Estimate"])
se_list_bonus <- lapply(clustered_se_bonus, function(x) x[, "Std. Error"])
pval_list_bonus <- lapply(clustered_se_bonus, function(x) x[, "Pr(>|t|)"])

# Clustered SE at country level For shirk tolerance models
clustered_se_shirk <- lapply(c(models_shirk_wms, list(multi_WMS_shirk)), function(model) {
  coeftest(model, vcov = vcovCL(model, cluster = ~countryname, data = wms_combined))
})

coef_list_shirk <- lapply(clustered_se_shirk, function(x) x[, "Estimate"])
se_list_shirk <- lapply(clustered_se_shirk, function(x) x[, "Std. Error"])
pval_list_shirk <- lapply(clustered_se_shirk, function(x) x[, "Pr(>|t|)"])

# Bonus Culture Prevalence Models Summary
stargazer(
  models_bonus_wms, 
  type = "latex",
  title = "Bonus Culture Prevalence (WMS) Regression Results",
  float = FALSE,
  dep.var.labels = "Bonus Culture Prevalence",
  covariate.labels = c("Relatively Low Responsibilism", 
                               "Relatively High Universalism ", 
                               "Relatively Individualistic", 
                               "Relatively Loose"),
  keep.stat = c("adj.rsq", "ser"),
  se = se_list_bonus,
  p = pval_list_bonus,
  omit = c("employment[A-Z]\\)", "factor\\(sic2\\)\\d+","Constant"),  # Regex to match all employment and sic2 dummies
  add.lines = list(
    c("Base Rate (Bonus Culture Prevalence)", 
      round(base_rates_bonus$base_rate_bonus_responsibilism, 3),
      round(base_rates_bonus$base_rate_bonus_universalism, 3),
      round(base_rates_bonus$base_rate_bonus_individualism, 3),
      round(base_rates_bonus$base_rate_bonus_tightloose, 3),
      round(base_rates_bonus$base_rate_bonus_combined, 3)),
    c("Fixed Effects (Firm Size)", "Yes", "Yes", "Yes", "Yes", "Yes"),
    c("Fixed Effects (Industry)", "Yes", "Yes", "Yes", "Yes", "Yes"),
    c("Clustered SEs", "Country Level", "Country Level", "Country Level", "Country Level", "Country Level"),
    c("Country-level Observations",
      wms_country_observations$Responsibilism,
      wms_country_observations$Universalism,
      wms_country_observations$Individualism,
      wms_country_observations$Tightness,
      wms_country_observations$Combined),
    c("Firm-level Observations",
      wms_firm_obs[1],
      wms_firm_obs[2],
      wms_firm_obs[3],
      wms_firm_obs[4],
      wms_firm_obs[5]),
    c("Spearman Correlation", 
      Bonus_spearman_values[["Spearman Correlation (Responsibilism)"]],
      Bonus_spearman_values[["Spearman Correlation (Universalism)"]],
      Bonus_spearman_values[["Spearman Correlation (Individualism)"]],
      Bonus_spearman_values[["Spearman Correlation (Tightness-Looseness)"]],
      "NA"),
    c("P-Value", 
      Bonus_spearman_values[["P-Value (Responsibilism)"]],
      Bonus_spearman_values[["P-Value (Universalism)"]],
      Bonus_spearman_values[["P-Value (Individualism)"]],
      Bonus_spearman_values[["P-Value (Tightness-Looseness)"]],
      "N/A")
  ),
  notes = NULL,
  out = "Tables/Regressions/bonus_wms_models_combined.tex"
)
  

# Shirk Tolerance Models Summary

stargazer(models_shirk_wms, 
          type = "latex",
          title = "Shirk Intolerance (WMS) Regression Results",
          float = FALSE,
          dep.var.labels = "Shirk Intolerance",
          covariate.labels = c("Relatively Low Responsibilism", 
                               "Relatively High Universalism ", 
                               "Relatively Individualistic", 
                               "Relatively Loose"),
          keep.stat = c("adj.rsq", "ser"),  # Keeps other stats but removes default obs
          omit = c("employment[A-Z]\\)", "factor\\(sic2\\)\\d+", "Constant"),  # Regex to match all employment and sic2 dummies
          se = se_list_shirk,
          p = pval_list_shirk,
          add.lines = list(
            c("Base Rate (Shirk Tolerance)", 
              round(base_rates_shirk$base_rate_shirk_responsibilism, 3),
              round(base_rates_shirk$base_rate_shirk_universalism, 3),
              round(base_rates_shirk$base_rate_shirk_individualism, 3),
              round(base_rates_shirk$base_rate_shirk_tightloose, 3),
              round(base_rates_shirk$base_rate_shirk_combined, 3)),
            c("Fixed Effects (Firm Size)", "Yes", "Yes", "Yes", "Yes", "Yes"),
            c("Fixed Effects (Industry)", "Yes", "Yes", "Yes", "Yes", "Yes"),
            c("Clustered SEs", "Country Level", "Country Level", "Country Level", "Country Level", "Country Level"),
            c("Country-level Observations",
              wms_country_observations$Responsibilism,
              wms_country_observations$Universalism,
              wms_country_observations$Individualism,
              wms_country_observations$Tightness,
              wms_country_observations$Combined),
            c("Firm-level Observations",
              wms_firm_obs[1],
              wms_firm_obs[2],
              wms_firm_obs[3],
              wms_firm_obs[4],
              wms_firm_obs[5]),
            c("Spearman Correlation", 
              Shirk_spearman_values[["Spearman Correlation (Responsibilism)"]],
              Shirk_spearman_values[["Spearman Correlation (Universalism)"]],
              Shirk_spearman_values[["Spearman Correlation (Individualism)"]],
              Shirk_spearman_values[["Spearman Correlation (Tightness-Looseness)"]], 
              "NA"),
            c("P-Value", 
              Shirk_spearman_values[["P-Value (Responsibilism)"]],
              Shirk_spearman_values[["P-Value (Universalism)"]],
              Shirk_spearman_values[["P-Value (Individualism)"]],
              Shirk_spearman_values[["P-Value (Tightness-Looseness)"]],
              "N/A")
          ),
          out = "Tables/Regressions/shirk_wms_models_combined.tex")

```



