---
title: "4. WMS Graphs"
output: html_notebook
Author: "Ayesha Zafar"
---

# Packages Used

```{r, message=FALSE}


library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(boot)
library(purrr)

```

# Load Dataset 

The master data is consolidated using the 1.Master_Data.RMD script. WMS data is extracted from the World Management Survey public data.

```{r, message=FALSE}

master_data <- read_excel("Data/Generated_Data/Master_Data.xlsx") %>%
  select(countryname, ISO_code, Responsibilism, tight_loose_cd)

wms_data <- read_csv("Data/Extracted_Data/wmsdata_2004_2015.csv") %>%
  select(country, talent2, talent3, sic2, employment) %>%  # Select relevant columns %>%
  rename("bonus_culture_prevalence_firm" = "talent2", 
         "shirk_tolerance_firm" = "talent3", 
         "countryname" = "country") 

wms_data$employment <- factor(wms_data$employment,
                                 levels = c("A) 50 to 100",
                                            "B) 101 to 250",
                                            "C) 251 to 500",
                                            "D) 501 to 1000",
                                            "E) 1000+"))

```

# Assigning Median-Based Cultural Categories to Firms

In this chunk Countries are classified as either "Low" or "High Responsibilism" and "Below" or "Above Median" on Cultural Tightness-Looseness, with "Unknown" assigned where values are missing.

```{r}

# Above/Below Median Responsibilism 


median_responsibilism <- master_data %>%
  filter(!is.na(Responsibilism)) %>%
  pull(Responsibilism) %>%
  median()

median_tight_loose <- master_data %>%
  filter(!is.na(tight_loose_cd)) %>%
  pull(tight_loose_cd) %>%
  median

wms_combined <- merge(wms_data, master_data, by = "countryname", all.x = TRUE) %>%

  mutate(Median_Responsibilism = ifelse(
    is.na(Responsibilism), "Unknown",
    ifelse(Responsibilism <= median_responsibilism, "Low Responsibilism", "High Responsibilism")
  ),
  Median_Tight_Loose = ifelse(
    is.na(tight_loose_cd), "Unknown",
    ifelse(tight_loose_cd >= median_tight_loose, "Above Median", "Below Median")
  ))

```

# Visualising High Management Practice Scores by Cultural Category

This chunk calculates and visualises the proportion of firms scoring 4 or 5 on two dimensions of management quality — Bonus Culture Prevalence and Shirk Intolerance — across cultural categories. It uses bootstrap resampling (1,000 iterations) to estimate 95% confidence intervals for each group defined by median Responsibilism and Tight-Looseness scores. The resulting bar plots illustrate how cultural context correlates with firm-level management outcomes.

```{r}


# Helper function to compute proportion of scores >= 4
boot_proportion <- function(data, indices) {
  d <- data[indices, ]
  mean(d$Score >= 4, na.rm = TRUE)
}

# Split the data by Median_Responsibilism and Category_Type
boot_results <- wms_combined %>%
  select(Median_Responsibilism, bonus_culture_prevalence_firm, shirk_tolerance_firm) %>%
  pivot_longer(cols = c(bonus_culture_prevalence_firm, shirk_tolerance_firm),
               names_to = "Category_Type", values_to = "Score") %>%
  filter(!is.na(Score)) %>%
  group_split(Median_Responsibilism, Category_Type) %>%
  map_df(function(df) {
    cat_type <- unique(df$Category_Type)
    resp_cat <- unique(df$Median_Responsibilism)
    
    # Run bootstrap
    set.seed(123)
    boot_out <- boot(df, statistic = boot_proportion, R = 1000)
    ci <- boot.ci(boot_out, type = "perc")$percent[4:5]
    
    tibble(
      Median_Responsibilism = resp_cat,
      Category_Type = cat_type,
      proportion = mean(df$Score >= 4),
      lower = ci[1],
      upper = ci[2]
    )
  }) %>%
  mutate(Median_Responsibilism = factor(
    Median_Responsibilism,
    levels = c("Low Responsibilism", "High Responsibilism", "Unknown")
  ))


plot1 <- ggplot(boot_results, aes(x = Median_Responsibilism, y = proportion, fill = Category_Type)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(aes(ymin = lower, ymax = upper),
                position = position_dodge(width = 0.8), width = 0.2) +
  scale_fill_manual(
    values = c("shirk_tolerance_firm" = "darkred", "bonus_culture_prevalence_firm" = "darkblue"),
    labels = c("shirk_tolerance_firm" = "Shirk Intolerance", "bonus_culture_prevalence_firm" = "Bonus Culture Prevalence")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    x = "Responsibilism Category",
    y = "Proportion Scoring 4 or 5",
    fill = "Category",
    title = "Proportion of Firms Scoring 4 or 5 by Responsibilism"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1, size = 11),  # Rotates and adjusts alignment
    axis.text.y = element_text(size = 11),
    axis.title = element_text(size = 12),
    plot.title = element_text(size = 14, face = "bold")
  )




# Split the data by Median_Cultural Tightness and Category_Type
boot_results_TL <- wms_combined %>%
  select(Median_Tight_Loose, bonus_culture_prevalence_firm, shirk_tolerance_firm) %>%
  pivot_longer(cols = c(bonus_culture_prevalence_firm, shirk_tolerance_firm),
               names_to = "Category_Type", values_to = "Score") %>%
  filter(!is.na(Score)) %>%
  group_split(Median_Tight_Loose, Category_Type) %>%
  map_df(function(df) {
    cat_type <- unique(df$Category_Type)
    resp_cat <- unique(df$Median_Tight_Loose)
    
    # Run bootstrap
    set.seed(123)
    boot_out <- boot(df, statistic = boot_proportion, R = 1000)
    ci <- boot.ci(boot_out, type = "perc")$percent[4:5]
    
    tibble(
      Median_Tight_Loose = resp_cat,
      Category_Type = cat_type,
      proportion = mean(df$Score >= 4),
      lower = ci[1],
      upper = ci[2]
    )
  }) %>%
  mutate(Median_Tight_Loose = factor(
    Median_Tight_Loose,
    levels = c("Below Median", "Above Median", "Unknown")
  ))


plot2 <- ggplot(boot_results_TL, aes(x = Median_Tight_Loose, y = proportion, fill = Category_Type)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(aes(ymin = lower, ymax = upper),
                position = position_dodge(width = 0.8), width = 0.2) +
  scale_fill_manual(
    values = c("shirk_tolerance_firm" = "darkred", "bonus_culture_prevalence_firm" = "darkblue"),
    labels = c("shirk_tolerance_firm" = "Shirk Intolerance", "bonus_culture_prevalence_firm" = "Bonus Culture Prevalence")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    x = "Tight-Loose Category",
    y = "Proportion Scoring 4 or 5",
    fill = "Category",
    title = "Proportion of Firms Scoring 4 or 5 by Cultural Looseness"
  ) +
  theme_minimal()

print(plot1)
print(plot2)

```


```{r}

pdf("Figures/WMS_Graph_1.pdf", width = 11, height = 8.5)   # All subsequent plots go into this PDF

print(plot1)
dev.off()

pdf("Figures/WMS_Graph_2.pdf", width = 11, height = 8.5)   # All subsequent plots go into this PDF
print(plot2)
dev.off()


```


