---
title: "Elasticity Graphs"
output: html_notebook
---

# Packages Load
This chunk loads the necessary libraries for data manipulation, bootstrapping, and visualization.
```{r}
library(dplyr)
library(tidyverse)
library(readxl)
library(boot)
library(purrr)
```

# Data Load
This chunk reads in the cleaned dataset containing country-level variables, including elasticity and cultural indicators.
```{r}
master_data <- read_excel("Data/Generated_Data/Master_Data.xlsx") 
```

# Median Split Variable Creation
This section computes median values for Responsibilism and Tightness-Looseness, and assigns countries to categories based on whether they fall above or below the median.
```{r}
median_responsibilism <- master_data %>%
  filter(!is.na(Responsibilism)) %>%
  pull(Responsibilism) %>%
  median() 

median_tight_loose <- master_data %>%
  filter(!is.na(tight_loose_cd)) %>%
  pull(tight_loose_cd) %>%
  median() 

master_data <- master_data %>%
  mutate(
    Responsibilism_category = if_else(is.na(Responsibilism), "Unknown",
                                      if_else(Responsibilism < median_responsibilism, "Above Median", "Below Median")),
    Tight_Loose_category = if_else(is.na(tight_loose_cd), "Unknown",
                                   if_else(tight_loose_cd > median_tight_loose, "Above Median", "Below Median"))
  ) %>%
  mutate(
    Responsibilism_category = factor(Responsibilism_category, levels = c("Below Median", "Above Median", "Unknown")),
    Tight_Loose_category = factor(Tight_Loose_category, levels = c("Below Median", "Above Median", "Unknown"))
  )
```

# Bootstrapping Setup
This function computes the mean elasticity for a resampled group, used to generate bootstrapped confidence intervals.
```{r}
boot_diff <- function(data, indices) {
  d <- data[indices, ]
  mean(d$elasticity_male, na.rm = TRUE)
}
```

# Bootstrap Plot for Responsibilism
This code estimates group-wise means for elasticity across cultural categories based on Responsibilism. Bootstrapped confidence intervals are generated for each group.
```{r}
boot_results_resp <- master_data %>%
  filter(!is.na(elasticity_male)) %>%
  group_split(Responsibilism_category) %>%
  map_df(function(df) {
    cat_name <- unique(df$Responsibilism_category)
    true_mean <- mean(df$elasticity_male, na.rm = TRUE)
    set.seed(123)
    boot_out <- boot(df, statistic = boot_diff, R = 1000)
    ci <- boot.ci(boot_out, type = "perc")$percent[4:5]
    tibble(
      Responsibilism_category = cat_name,
      mean = true_mean,
      lower = ci[1],
      upper = ci[2]
    )
  })

plot1 <- ggplot(boot_results_resp, aes(x = Responsibilism_category, y = mean)) +
  geom_point(size = 3, color = "#08519c") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1, color = "#08519c") +
  theme_minimal() +
  labs(
    x = "Responsibilism",
    y = "Mean Male Labour Supply Elasticity",
    title = "Male Labour Supply Elasticity by Responsibilism"
  ) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11)
  )

print(plot1)
```

# Bootstrap Plot for Tightness-Looseness
This code does the same as the previous chunk, but categorizes countries based on Tightness-Looseness cultural scores.
```{r}
boot_results_tl <- master_data %>%
  filter(!is.na(elasticity_male)) %>%
  group_split(Tight_Loose_category) %>%
  map_df(function(df) {
    cat_name <- unique(df$Tight_Loose_category)
    true_mean <- mean(df$elasticity_male, na.rm = TRUE)
    set.seed(123)
    boot_out <- boot(df, statistic = boot_diff, R = 1000)
    ci <- boot.ci(boot_out, type = "perc")$percent[4:5]
    tibble(
      Tight_Loose_category = cat_name,
      mean = true_mean,
      lower = ci[1],
      upper = ci[2]
    )
  })

plot2 <- ggplot(boot_results_tl, aes(x = Tight_Loose_category, y = mean)) +
  geom_point(size = 3, color = "#08519c") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1, color = "#08519c") +
  theme_minimal() +
  labs(
    x = "Cultural Looseness",
    y = "Mean Male Labour Supply Elasticity",
    title = "Male Labour Supply Elasticity by Cultural Looseness"
  ) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11)
  )

print(plot2)
```

# Export Plots to PDF
This chunk saves each plot to a landscape-oriented PDF file for use in reports.
```{r}
pdf("Figures/Elasticity_Graphs_1.pdf", width = 11, height = 8.5)
print(plot1)
dev.off()

pdf("Figures/Elasticity_Graphs_2.pdf", width = 11, height = 8.5)
print(plot2)
dev.off()
```
