---
title: "7.TFP_Graphs"
output: html_notebook
---

# Packages Load
```{r}
library(dplyr)
library(tidyverse)
library(readxl)
library(boot)
library(purrr)
```

# Data Load

This chunk reads in the cleaned master dataset from Excel, which contains country-level variables including cultural indicators and productivity metrics.

```{r}
master_data <- read_excel("Data/Generated_Data/Master_Data.xlsx") 
```

# Median Split Variable Creation

This section computes the median values for Responsibilism and Tightness-Looseness, then assigns each country to an "Above Median", "Below Median", or "Unknown" group based on their cultural score.

```{r}
median_responsibilism <- master_data %>%
  filter(!is.na(Responsibilism)) %>%
  pull(Responsibilism) %>%
  median() 

median_tight_loose <- master_data %>%
  filter(!is.na(tight_loose_cd)) %>%
  pull(tight_loose_cd) %>%
  median() 

master_data <- master_data %>%
  mutate(
    Responsibilism_category = if_else(is.na(Responsibilism), "Unknown",
                                      if_else(Responsibilism <= median_responsibilism, "Above Median", "Below Median")),
    Tight_loose_category = if_else(is.na(tight_loose_cd), "Unknown",
                                   if_else(tight_loose_cd >= median_tight_loose, "Above Median", "Below Median"))
  ) %>%
  mutate(
    Responsibilism_category = factor(Responsibilism_category, levels = c("Below Median", "Above Median", "Unknown")),
    Tight_loose_category = factor(Tight_loose_category, levels = c("Below Median", "Above Median", "Unknown"))
  )
```

# Bootstrapping Setup

Here we define the function to compute the mean of total factor productivity, which will be used in bootstrapping to estimate confidence intervals.

```{r}
boot_ci_tfp <- function(data, indices) {
  d <- data[indices, ]
  mean(d$total_factor_productivity, na.rm = TRUE)
}
```

# Bootstrap Plot for Responsibilism

This code performs bootstrapping to generate confidence intervals for true group means of TFP (not bootstrapped means).

```{r}
boot_results_resp <- master_data %>%
  filter(!is.na(total_factor_productivity)) %>%
  group_split(Responsibilism_category) %>%
  map_df(function(df) {
    cat_name <- unique(df$Responsibilism_category)
    set.seed(123)
    boot_out <- boot(df, statistic = boot_ci_tfp, R = 1000)
    ci <- boot.ci(boot_out, type = "perc")$percent[4:5]
    tibble(
      Responsibilism_category = cat_name,
      mean = mean(df$total_factor_productivity, na.rm = TRUE),  # True mean
      lower = ci[1],
      upper = ci[2]
    )
  })

plot1 <- ggplot(boot_results_resp, aes(x = Responsibilism_category, y = mean)) +
  geom_point(size = 3, color = "#08519c") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1, color = "#08519c") +
  theme_minimal() +
  labs(
    x = "Responsibilism",
    y = "Mean Total Factor Productivity",
    title = "Total Factor Productivity by Responsibilism"
  ) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11)
  )

print(plot1)
```

# Bootstrap Plot for Tightness-Looseness

Similar to the previous chunk, this performs bootstrapping for TFP grouped by Tightness-Looseness categories and plots true means with percentile confidence intervals.

```{r}
boot_results_tl <- master_data %>%
  filter(!is.na(total_factor_productivity)) %>%
  group_split(Tight_loose_category) %>%
  map_df(function(df) {
    cat_name <- unique(df$Tight_loose_category)
    set.seed(123)
    boot_out <- boot(df, statistic = boot_ci_tfp, R = 1000)
    ci <- boot.ci(boot_out, type = "perc")$percent[4:5]
    tibble(
      Tight_loose_category = cat_name,
      mean = mean(df$total_factor_productivity, na.rm = TRUE),  # True mean
      lower = ci[1],
      upper = ci[2]
    )
  })

plot2 <- ggplot(boot_results_tl, aes(x = Tight_loose_category, y = mean)) +
  geom_point(size = 3, color = "#08519c") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1, color = "#08519c") +
  theme_minimal() +
  labs(
    x = "Cultural Looseness",
    y = "Mean Total Factor Productivity",
    title = "Total Factor Productivity by Cultural Looseness"
  ) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11)
  )

print(plot2)
```

# Export Plots to PDF

This final chunk saves both plots to a PDF file so they can be used in reports or included in LaTeX documents.

```{r}

pdf("Figures/TFP_Graphs_1.pdf", width = 11, height = 8.5)   # All subsequent plots go into this PDF

print(plot1)
dev.off()

pdf("Figures/TFP_Graphs_2.pdf", width = 11, height = 8.5)   # All subsequent plots go into this PDF
print(plot2)
dev.off()
```
